---
title: "Recipe Machine Learning"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(reshape2)
library(dplyr)
library(ggplot2)
```


# Ratatouille Recipe Dataset

I load my simulated recipes and convert all the skills and tools columns to categorical

```{r}
recipedf <- read.csv("../data/generated_recipes.csv")

getColNames <- function(df,colpat)
{
  subset(names(df),grepl( colpat , names( df ) ))
}
catNames <- getColNames(recipedf,"S_|T_")
recipedf[catNames]<-lapply(catNames, function(x) {factor(recipedf[,x])})


head(recipedf,10)
```


# Test/Train split

I now do an 80/20 train/test split before training the machine to identify skills.

```{r}
library(caret)
intrain<-createDataPartition(recipedf$RID,p=0.8,list=FALSE)
training<-recipedf[intrain,]
testing<-recipedf[-intrain,]
```

I am going to fit models to each one of the "S" columns. 

```{r}
library(arm)
library(pbapply)
getPred <- function(training,testing,inputName, ScolName){
  # With a single input, train and predict the outcome for that column
  formula1 <- as.formula(paste(ScolName,"~", paste(getColNames(training,inputName), collapse = "+")))
  LRfit <- bayesglm(formula1, training,family="binomial")
  lrpredictions<-predict(LRfit,testing,type="response")
  return(lrpredictions)
}

getResults<- function(training,testing,inputCol, outputCol){
  # Iterate through all columns to get predictions
  sNames<-getColNames(training,outputCol)
  
  probcols<-suppressWarnings(pbsapply(sNames, function(x) {getPred(training,testing,inputCol,x)}))
  colnames(probcols) <- paste0(sNames,".prob")
  predcols <- 1*(probcols>0.5)
  m1<-as.matrix(sapply(testing[sNames],function(x) as.numeric(as.character(x))))
  accCols <- 1-1*xor(m1,predcols)
  predcols <- apply(predcols,2,FUN=function(x) {factor(x)})
  colnames(accCols) <- paste0(sNames,".acc")
  
  colnames(predcols) <- paste0(sNames,".pred")
  
  testoutS<-cbind(testing[sNames],predcols,accCols,probcols)
  return(testoutS)
}
testoutS <- getResults(training,testing,"I_","S_")
head(testoutS)
```
How good did we do? This is a measure of the perfect matches.
```{r}
colMeans(testoutS[,grep(".acc",names(testoutS))])
```

Now predict the T columns based on the S column predictions

```{r}
sNames<-getColNames(testing,"S_")
# Replace the training values with our predictions
testingSnew <- testing
testingSnew[sNames] <- NULL
testingSnew[paste0(sNames,".pred")] <- testoutS[paste0(sNames,".pred")]

# Rename the training columns to match
trainingSnew <- training
trainingSnew[paste0(sNames,".pred")] <- trainingSnew[sNames]
trainingSnew[sNames] <- NULL

testoutT <- getResults(trainingSnew,testingSnew,"I_|S_","T_")
colMeans(testoutT[,grep(".acc",names(testoutT))])
```

Checking against our predictions based on the original values:
```{r}
testoutT2 <- getResults(training,testing,"I_|S_","T_")
colMeans(testoutT2[,grep(".acc",names(testoutT2))])
```

So we did significantly worse in predicting "T_" when we used the predictions from the "S_" data.


